Learning Auditory Similarities Between Instrumental Playing Techniques

### 2019-10-31 paper/paper.tex
fix sections

\ja{These section numbers aren't showing up since we're not numbering the sections (per the style guide).}
Section \ref{sec:soa} reviews recent research in the computational modeling of musical timbre.
Section \ref{sec:survey} describes our data collection procedure for auditory similarities across playing techniques.
Section \ref{sec:method} presents the technical components of our machine listening system, namely joint time--frequency scattering and large-margin nearest neighbors.
Section \ref{sec:results} reports the results of an ablation study of our system.
Section \ref{sec:discussion} discusses the implications of our findings for future research on timbral similarity.\footnote{Reproducible research statement: the implementation of the proposed model and the experimental protocol of this paper are available online, alongside anonymized data from human subjects:  \url{https://github.com/mathieulagrange/paperPlayingTechniquesSimilarityLearning}} %TODO: simplify this URL to lostanlen2020jasmp

>>>>

\ml{reword.}
Section \nameref{sec:soa} reviews recent research in the computational modeling of musical timbre.
Section \nameref{sec:survey} describes our data collection procedure for auditory similarities across playing techniques.
Section \nameref{sec:method} presents the technical components of our machine listening system, namely joint time--frequency scattering and large-margin nearest neighbors.
Section \nameref{sec:results} reports the results of an ablation study of our system.
Section \nameref{sec:discussion} discusses the implications of our findings for future research on timbral similarity.\footnote{Reproducible research statement: the implementation of the proposed model and the experimental protocol of this paper are available online, alongside anonymized data from human subjects:  \url{https://github.com/mathieulagrange/paperPlayingTechniquesSimilarityLearning}} %TODO: simplify this URL to lostanlen2020jasmp
